---
title: "Dashboard: Trucks Sold Forecast Model"
output: 
  flexdashboard::flex_dashboard:
    orientation: column
    vertical_layout: fill
    source_code: NULL
    logo: docs/logo.png
    social: menu
    navbar:
        - { icon: "fa-github", href: "https://github.com/schoulten", align: right }
        - { icon: "fa-linkedin", href: "https://www.linkedin.com/in/schoulten/", align: right }
        - { icon: "fa-at", href: "mailto:fernando@fortietwo.com", align: right }
---

<script>
$('.navbar-logo').wrap('<a href="https://fortietwo.com/" target=_blank>');
</script>

<style>                     
.navbar {
  background-color:#282f6b;
}
.navbar-inverse .navbar-nav > li > a:hover,
.navbar-inverse .navbar-nav > li > a:focus {
  color: #ffffff;
    background-color: #ffffff21;
}
.navbar-inverse .navbar-nav > .active > a,
.navbar-inverse .navbar-nav > .active > a:hover,
.navbar-inverse .navbar-nav > .active > a:focus {
  color: #ffffff;
    background-color: #ffffff21;
}
.navbar-inverse .navbar-toggle:hover,
.navbar-inverse .navbar-toggle:focus {
  background-color: #ffffff21;
}
.navbar-inverse .navbar-nav > .open > a,
.navbar-inverse .navbar-nav > .open > a:hover,
.navbar-inverse .navbar-nav > .open > a:focus {
  background-color: #ffffff21;
    color: #ffffff;
}
.dropdown-menu > li > a:hover,
.dropdown-menu > li > a:focus {
  text-decoration: none;
  color: #ffffff;
    background-color: #282f6b;
}
.dropdown-menu > .active > a,
.dropdown-menu > .active > a:hover,
.dropdown-menu > .active > a:focus {
  color: #ffffff;
    text-decoration: none;
  outline: 0;
  background-color: #282f6b;
}
.nav-tabs-custom > .nav-tabs > li.active {
  border-top-color: #282f6b;
}
</style>

```{r global, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_knit$set(progress = TRUE)
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE)
```



Overview
=====================================


Column {data-width=600}
-------------------------------------

### Fanchart {.no-title}

```{r fanchart, fig.width=9.5}
plot_fanchart
```

### Accuracy {.no-title}

```{r accuracy, fig.width=9.5}
plt_rmse
```


Column
-------------------------------------

### Point forecast {.no-title}

```{r points}
frcst_dt
```


### Accuracy metrics {.no-title}

```{r metrics}
acc_dt
```



Trucks Sold Forecast Model {.sidebar data-width=250}
=====================================

#### **Trucks Sold Forecast Model**
This dashboard shows the **key results of forecast models** for the Number of Trucks Sold, through time series econometric models using the `R` language.

**About the workflow**:

1) Data processing (ETL)<br>
2) Exploratory Data Analysis (EDA)<br>
3) Modeling with a cross-validation scheme<br>
4) Automated final model choice<br>
5) Refit and diagnostics with full sample<br>
6) Out-of-sample forecasts<br>


**Last update**: `r Sys.Date()`.
